### 2009-09-01 latex/paper1/contents.tex
pdf

choose event with probabilities (p, q, r)
event 1:
  choose w within V according to f(x) = din + in-degree(x)
  add new vertex v to the module of w
  add edge from v to w
event 2:
  choose w within V according to f(x) = dout + out-degree(x)
  add new vertex v to the module of w
  add edge from w to v
event 3:
  choose v within V according to f(x) = dout + out-degree(x)
  choose case with probabilities (mu, 1 - mu)
  case 1: # out
    choose w within neighbor-modules(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
  case 2:
    choose w within module(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
end

>>>>

choose event with probabilities (p, q, r)
event 1:
  choose w within V according to f(x) = din + in-degree(x)
  add new vertex v to the module of w
  add edge from v to w
event 2:
  choose w within V according to f(x) = dout + out-degree(x)
  add new vertex v to the module of w
  add edge from w to v
event 3:
  choose v within V according to f(x) = dout + out-degree(x)
  choose case with probabilities (mu, 1 - mu)
  case 1: % out
    choose w within neighbor-modules(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
  case 2:
    choose w within module(v) - neighbors(v) according to f(x) = din + in-degree(x)
    add edge from v to w
end
